\pagebreak[1]
\clearpage
\thispagestyle{plain}

\begin{center}
	\vspace*{1.5cm}
	{\Large \bfseries ACKNOWLEDGEMENTS}
	\vspace{1.5cm}
\end{center}

This Bachelor's Thesis is the result of several months of dedication and hard work. However, it could not have been possible without the support of many people I would like to give recognition to.

First of all, to my supervisor Ignacio Esteban ``Nacho'', who has always given me his unconditional help, support, advice and patience. He has invested a lot of time teaching me how to perform measurements in and out of the laboratory, to organise my work and the basis of radar knowledge of which I am extremely grateful. Through Nacho, I have been able to meet all my colleagues of the GMR research group, who have also provided me with lots of encouragement and good lunches together.

This Thesis has been developed under the direction of professor Jesús Grajal, who I thank for his constant advice, for always having all the needed resources for the project at my disposal and for giving me the opportunity to develop this project at GMR through an scholarship.

To my classmates who became my dearest friends, to all of ``la \textit{piña}'' ---specially Cristina--- and to the friends I met in the electronics intensification and in the IEEE Student Branch: Mavi, Miguel and Diego. I thank every single one of them for such wonderful years full of amazing moments and for their kind support even when things were not moving forward. With their help and company, the journey through the ETSIT is much less frustrating.

To Blanca, for all the lessons she teaches me and for her unconditional support and motivation, always being there when I needed it.

Finally, I would like to thank my family for their love and encouragement. Specially to my parents and my brother, who have always motivated and supported me throughout my whole life, allowing me to become who I am thanks to them. Sergio, now it's your turn.





